%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {DevOps \& Cloud Engineer} % Job title
    {The Vietnam Technological and Commercial Joint Stock Bank (TECHCOMBANK)} % Organization
    {Hanoi, Vietnam} % Location
    {Apr. 2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Design and implement AWS Landing Zone using AWS Control Tower service.}
        \item {Provision and manage multiple AWS accounts' infrastructure using Terraform.}
        \item {Migrate applications from On-premises to Cloud with a lot of differential complex architect designs.}
        \item {Build toolchain for Infrastructure as Code.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {DevOps Engineer} % Job title
    {VietNamNet Online Newspaper} % Organization
    {Hanoi, Vietnam} % Location
    {May. 2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Build and maintain Kubernetes infrastructure following the GitOps pattern.}
        \item {Build and maintain the CICD process.}
        \item {Configure logging and monitoring for all systems.}
        \item {Maintain backup/restore strategies, monthly restore testing.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {DevOps \& Cloud Engineer} % Job title
    {Vinsmart Research and Manufacture Joint Stock Company (VINGROUP)} % Organization
    {Hanoi, Vietnam} % Location
    {Mar. 2019 - Apr. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Build and maintain all Vinsmart's information technology infrastructure from scratch.}
        \item {Design, implement, administrating, operating, tuning the cloud-native infrastructure as Kubernetes to serve many applications.}
        \item {Design, implement, administrating, operating, cost optimization for Azure infrastructure.}
        \item {Migrate legacy applications into containers and Kubernetes, setup and manage CI/CD.}
        \item {Troubleshoot system issues related to CI/CD process, server problems, network, DNS, etc.}
        \item {Implement applications in multiple regions.}
        \item {Implement, administrating, and operating, tuning SQL Server, MySQL, MongoDB.}
        \item {Resource capacity planning of CPU, Memory, Storage.}
        \item {Patching, updating, security hardening for applications and servers.}
        \item {Maintain backup/restore strategies, monthly restore testing.}
        \item {Support other DevOps teams to implement, go-live/public applications.}
        \item {Mentoring and training other employees.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Database Administrator} % Job title
    {The Vietnam Technological and Commercial Joint Stock Bank (TECHCOMBANK)} % Organization
    {Hanoi, Vietnam} % Location
    {Nov. 2017 - Mar. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Administering, monitoring, and maintaining the database-related products and solutions as Oracle Database, RAC, Data Guard, Transparent Data Encryption, Microsoft SQL Server, …}
        \item {Installing and upgrading the Oracle Database server and application tools.}
        \item {Tuning Production databases for performance optimization.}
        \item {Allocating system storage and planning future storage requirements for the database system.}
        \item {Writing the security hardening documents for system operation and databases.}
        \item {Managing User privileges \& Roles.}
        \item {Setting up jobs for monitoring the operation system, databases and setting up daily and weekly backup using Veritas NetBackup.}
        \item {Auditing the database objects and system privileges.}
        \item {Work in conjunction with application developers, architects, and systems administrators.}
        \item {Contacting Oracle for technical support.}
        \item {Support end-users to resolve requests.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Database Administrator} % Job title
    {August Technology and Application Joint Stock Company (AT\&A)} % Organization
    {Hanoi, Vietnam} % Location
    {Mar. 2016 - Sep. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Troubleshooting incidents and request fulfillment support.}
        \item {Monthly database health check report.}
        \item {Installation, configuration, maintenance, and upgrades Oracle products.}
        \item {Create backup and recovery plans and procedures.}
        \item {Monitor performance of the database and operating system.}
        \item {Performing ongoing tuning of the database instances.}
        \item {Writing and maintaining database documentation.}
        \item {Capacity planning creation.}
        \item {Patch management and version control.}
        \item {Administering all database objects, including tables, clusters, indexes, materialized views, sequences, packages, and procedures.}
        \item {Managing the security and disaster recovery aspects of the database.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
